---
title: "Ching’s RMD"
author: "Ching"
date: "September 27, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

amen_Air_conditioning	4.01709402			
amen_Self_Check-In	3.76068376			
amen_Gym	3.11965812			
amen_Lockbox
amen_Suitable_for_events	2.29344729			
amen_Private_entrance	1.05413105			
amen_Private_living_room	1.03988604			
amen_Pool	0.52706553			
amen_Doorman_Entry
```{r}
library(dplyr)
library(plyr)
library(ggplot2)
amen<-select(data_short,contains("amen_"))
amen1<-rename(amen,c("amen_Internet"="Internet","amen_Wireless_Internet"="Wifi","amen_Heating"="Heating","amen_Kitchen"="Kitchen","amen_Essentials"="Essentials","amen_Washer"="Washer","amen_Smoke_detector"="Smoke_detector","amen_Shampoo"="Shampoo","amen_Hangers"="Hangers","amen_Iron"="Iron","amen_TV"="TV","amen_Hair_dryer"="Hair_dryer","amen_Carbon_monoxide_detector"="Carbon_monoxide_detector","amen_Laptop_friendly_workspace"="Laptop_friendly","amen_Family/kid_friendly"="Family_friendly","amen_Buzzer/wireless_intercom"="Buzzer_wireless","amen_Dryer"="Dryer","amen_First_aid_kit"="First_aid_kit","amen_Elevator_in_building"="Elevator_in_building","amen_Fire_extinguisher"="Fire_extinguisher","amen_24-hour_check-in"="24_hour_check_in","amen_Free_parking_on_premises"="Free_parking","amen_Breakfast"="Breakfast","amen_Cable_TV"="Cable_TV","amen_Lock_on_bedroom_door"="Lock_on_bedroom_door","amen_Safety_card"="Safety_card","amen_Smoking_allowed"="Smoking_allowed","amen_Pets_live_on_this_property"="Pets_live_here","amen_Hot_tub"="Hot_tub","amen_Wheelchair_accessible"="Wheelchair_accessible","amen_Pets_allowed"="Pets_allowed","amen_Indoor_fireplace"="Indoor_fireplace","amen_Doorman"="Doorman","amen_Keypad"="Keypad","amen_Free_parking_on_street"="Free_parking_on_street","amen_Paid_parking_off_premises"="Paid_parking","amen_Smartlock"="Smartlock","amen_Washer_/_Dryer"="Washer_Dryer","amen_Air_conditioning"="Air_con","amen_Self_Check-In"="Self_Check-In","amen_Gym"="Gym","amen_Lockbox"="Lockbox","amen_Suitable_for_events"="Suitable_for_events","amen_Private_entrance"="Private_entrance","amen_Private_living_room"="Private_living_room","amen_Pool"="Pool","amen_Doorman_Entry"="Doorman_Entry"))
amen_name<-colnames(amen1)
number<-colMeans(amen1[, (1:53)], na.rm=TRUE)*100
data<-as.data.frame(amen_name)
data$number=number
data_remove_amen<-data[-c(17,18,21,36,45,51),]
arrange(data_remove_amen,desc(number))

```

#Amenity
In AirBnB, landlords offer different amenities for the tenants, including Wifi, kitchen, washer, even shampoo, and etc, and those facilities will be showed in the webpages for tenants’ references. Out of 53,844 offerings of rooms in London, internet connections are the most important elements in room. There are 97% of the rooms offering Wifi and internet connection. Besides, some general amenities for houses such as heating facilities (96%), kitchens (91%), essentials (85%), washers (81%), shampoo(62%), hangers (61%), and Iron (56%), will often be provided in houses/rooms. However, in London, most of the offerings don’t allow their customers to smoke and to bring their pets with them. 77% of rooms are with smoke detectors, and only 10% of rooms are smoking allowed and pets allowed. Due to the weather in London, air-con facility seems not important, but this will be a must in most of the Asian countries. 

```{r}
ggplot(data_remove_amen,aes(x =reorder(amen_name, -number),y=number))+geom_col()+theme(axis.text = element_text(angle= 90, hjust = 1))+labs(x = "amenity",y="%")
```

# 


```{r}
library(plyr)
rating<-list("number_of_reviews","review_scores_rating","review_scores_value")
rating1<-unlist(rating)
amen_list<-list(amen_name)
amen_list1<-unlist(amen_list)
data.cor<-select(data_short,contains("amen_"),price,price_log,number_of_reviews,review_scores_rating,review_scores_value,review_scores_cleanliness)%>%filter(!is.na(number_of_reviews),!is.na(review_scores_rating),!is.na(review_scores_value),!is.na(review_scores_cleanliness))
data_amen<-rename(data.cor,c("amen_Internet"="Internet","amen_Wireless_Internet"="Wifi","amen_Heating"="Heating","amen_Kitchen"="Kitchen","amen_Essentials"="Essentials","amen_Washer"="Washer","amen_Smoke_detector"="Smoke_detector","amen_Shampoo"="Shampoo","amen_Hangers"="Hangers","amen_Iron"="Iron","amen_TV"="TV","amen_Hair_dryer"="Hair_dryer","amen_Carbon_monoxide_detector"="Carbon_monoxide_detector","amen_Laptop_friendly_workspace"="Laptop_friendly_workspace","amen_Family/kid_friendly"="Family_kid_friendly","amen_Buzzer/wireless_intercom"="Buzzer_wireless_intercom","amen_Dryer"="Dryer","amen_First_aid_kit"="First_aid_kit","amen_Elevator_in_building"="Elevator_in_building","amen_Fire_extinguisher"="Fire_extinguisher","amen_24-hour_check-in"="24_hour_check_in","amen_Free_parking_on_premises"="Free_parking_on_premises","amen_Breakfast"="Breakfast","amen_Cable_TV"="Cable_TV","amen_Lock_on_bedroom_door"="Lock_on_bedroom_door","amen_Safety_card"="Safety_card","amen_Smoking_allowed"="Smoking_allowed","amen_Pets_live_on_this_property"="Pets_live_on_this_property","amen_Hot_tub"="Hot_tub","amen_Wheelchair_accessible"="Wheelchair_accessible","amen_Pets_allowed"="Pets_allowed","amen_Indoor_fireplace"="Indoor_fireplace","amen_Doorman"="Doorman","amen_Keypad"="Keypad","amen_Free_parking_on_street"="Free_parking_on_street","amen_Paid_parking_off_premises"="Paid_parking_off_premises","amen_Smartlock"="Smartlock","amen_Washer_/_Dryer"="Washer_Dryer","amen_Air_conditioning"="Air_con","amen_Self_Check-In"="Self_Check-In","amen_Gym"="Gym","amen_Lockbox"="Lockbox","amen_Suitable_for_events"="Suitable_for_events","amen_Private_entrance"="Private_entrance","amen_Private_living_room"="Private_living_room","amen_Pool"="Pool","amen_Doorman_Entry"="Doorman_Entry"))
data_amen1<-filter(data_amen,price<=150)
data_amen2<-filter(data_amen1,review_scores_rating>=80)
data_amen3<-filter(data_amen1,review_scores_value>=8)
data_amen4<-filter(data_amen1,review_scores_cleanliness>=8)
data_amen5<-filter(data_amen1,number_of_reviews<=50)

```
#Key ameniteis to influence the price

There are around 47 offers of amenities in the AirBnB in London. Out of 47 amenities offerings, we found 7 amenities may influence the price, including some home essentials such as kitchens, TVs, dryers, and washers, facilities like elevators or whether it’s a family-kid friendly environment as well as whether it provides lock on the bedroom door. The price of the accommodation with TVs, elevators, dryers and washers is higher than those don’t, especially for TV, which may lead to higher overall rating and perceived value from customers (Please refer to the plot between the amenity and rating below. Since most of the ratings are above 80 or 8, we do filter the rooms with rating more than 80 or 8 to see the difference. People tend to rate the room among higher range, mostly above 90 or 9. Therefore, some drop from 10 to 9 should already be significant.)  However, it seems the market doesn’t value those accommodations with family-kid friendly environment and kitchen. Their prices are slightly lower than those without those amenities. Probably, those amenities linked to more work and noisy. Another interesting finding is the room without the lock can may have higher price than others, which may be reasoned that the room with lock may mainly in more unsafe regions.


```{r}
ggplot(data_amen1,aes(x=Family_kid_friendly,y=price))+geom_boxplot()
ggplot(data_amen1,aes(x=TV,y=price))+geom_boxplot()
ggplot(data_amen1,aes(x=Elevator_in_building,y=price))+geom_boxplot()
ggplot(data_amen1,aes(x=Dryer,y=price))+geom_boxplot()
ggplot(data_amen1,aes(x=Kitchen,y=price))+geom_boxplot()
ggplot(data_amen1,aes(x=Washer,y=price))+geom_boxplot()
ggplot(data_amen1,aes(x=Lock_on_bedroom_door,y=price))+geom_boxplot()
```

```{r}

ggplot(data_amen2,aes(x=TV,y=review_scores_rating))+geom_boxplot()
ggplot(data_amen2,aes(x=Elevator_in_building,y=review_scores_rating))+geom_boxplot()
ggplot(data_amen2,aes(x=Family_kid_friendly,y=review_scores_rating))+geom_boxplot()
ggplot(data_amen2,aes(x=Dryer,y=review_scores_rating))+geom_boxplot()
ggplot(data_amen2,aes(x=Kitchen,y=review_scores_rating))+geom_boxplot()
ggplot(data_amen2,aes(x=Washer,y=review_scores_rating))+geom_boxplot()
ggplot(data_amen2,aes(x=Lock_on_bedroom_door,y=review_scores_rating))+geom_boxplot()


```

```{r}
ggplot(data_amen3,aes(x=TV,y=review_scores_value))+geom_boxplot()

```

#Rent
With no doubt, London is one of the most expensive city to live, and more buildings are built to rent (1). AirBnB is the service that encourages the people to rent their vacant rooms to people, and some of the recent news and articles indicated the relationship between the rent and AirBnB such as the issue if AirBnB push the rent higher (2/3), and the issue that if the AirBnB increase the sub-letting cases. (4). Therefore, this triggers us to explore the relationship between rent and AirBnB price of London in this report. Thus, we would like to map the rent price with the AirBnB price. Searching for the big property websites such as Rightmove or Zoopla, we found one website called “Find Property”(5), which utilizes the data from Zoopla and provide the rent and selling price for each region by 217 zip code, from BR1 to WD25. Then, we map the rent price with AirBnB price based on zip code in the original dataset.
[put the plot of the map/plot with rental price]


1.	https://www.theguardian.com/business/2017/sep/14/build-to-rent-the-solution-to-britains-housing-crisis
2.	https://www.standard.co.uk/news/london/airbnb-chief-we-are-not-to-blame-for-rising-london-rents-a3357136.html
3.	http://uk.businessinsider.com/statistics-data-airbnb-rent-prices-2016-10
4.	https://www.mountgrangeheritage.co.uk/property-market-blog/airbnb-affected-londons-rental-market/
5. https://www.findproperly.co.uk/london/postcode/#.WdvonHeZNn4


#---------------------------------------------------------------------------#



```{r}
ggplot(data_amen4,aes(x=amen_TV,y=review_scores_cleanliness))+geom_boxplot()
ggplot(data_amen4,aes(x=amen_Elevator_in_building,y=review_scores_cleanliness))+geom_boxplot()
ggplot(data_amen4,aes(x=amen_Family_kid_friendly,y=review_scores_cleanliness))+geom_boxplot()
ggplot(data_amen4,aes(x=amen_Dryer,y=review_scores_cleanliness))+geom_boxplot()
ggplot(data_amen4,aes(x=amen_Kitchen,y=review_scores_cleanliness))+geom_boxplot()
ggplot(data_amen4,aes(x=amen_Washer,y=review_scores_cleanliness))+geom_boxplot()
ggplot(data_amen4,aes(x=amen_Lock_on_bedroom_door,y=review_scores_cleanliness))+geom_boxplot()
```

```{r}
ggplot(data_amen5,aes(x=amen_Family_kid_friendly,y=number_of_reviews))+geom_boxplot()
ggplot(data_amen5,aes(x=amen_TV,y=number_of_reviews))+geom_boxplot()
ggplot(data_amen5,aes(x=amen_Elevator_in_building,y=number_of_reviews))+geom_boxplot()
ggplot(data_amen5,aes(x=amen_Dryer,y=number_of_reviews))+geom_boxplot()
ggplot(data_amen5,aes(x=amen_Kitchen,y=number_of_reviews))+geom_boxplot()
ggplot(data_amen5,aes(x=amen_Washer,y=number_of_reviews))+geom_boxplot()
ggplot(data_amen5,aes(x=amen_Lock_on_bedroom_door,y=number_of_reviews))+geom_boxplot()
```



```{r}
NSR<-lm(review_scores_rating~amen_Wireless_Internet
+amen_Kitchen
+amen_Washer
+amen_Smoke_detector
+amen_Laptop_friendly_workspace
+amen_TV
+amen_Internet
+amen_Free_parking_on_premises
+amen_Elevator_in_building
+amen_Heating
+amen_Family_kid_friendly
+amen_Essentials
+amen_Carbon_monoxide_detector
+amen_Hangers
+amen_Cable_TV
+amen_Indoor_fireplace
+amen_Dryer
+amen_First_aid_kit
+amen_24_hour_check_in
+amen_Hair_dryer
+amen_Iron
+amen_Breakfast
+amen_Shampoo
+amen_Pets_allowed
+amen_Gym
+amen_Pets_live_on_this_property
+amen_Suitable_for_events
+amen_Private_living_room
+amen_Private_entrance
+amen_Lock_on_bedroom_door
+amen_Fire_extinguisher
+amen_Smoking_allowed
+amen_Safety_card
+amen_Hot_tub
+amen_Buzzer_wireless_intercom
+amen_Wheelchair_accessible
+amen_Air_conditioning
+amen_Doorman
+amen_Self_Check_In
+amen_Smartlock
+amen_Keypad
+amen_Lockbox
+amen_Doorman_Entry
+amen_Pool
+amen_Washer_Dryer
+amen_Free_parking_on_street
+amen_Paid_parking_off_premises
,data=data_amen)
summary(NSR)

NSV<-lm(review_scores_value~amen_Wireless_Internet
+amen_Kitchen
+amen_Washer
+amen_Smoke_detector
+amen_Laptop_friendly_workspace
+amen_TV
+amen_Internet
+amen_Free_parking_on_premises
+amen_Elevator_in_building
+amen_Heating
+amen_Family_kid_friendly
+amen_Essentials
+amen_Carbon_monoxide_detector
+amen_Hangers
+amen_Cable_TV
+amen_Indoor_fireplace
+amen_Dryer
+amen_First_aid_kit
+amen_24_hour_check_in
+amen_Hair_dryer
+amen_Iron
+amen_Breakfast
+amen_Shampoo
+amen_Pets_allowed
+amen_Gym
+amen_Pets_live_on_this_property
+amen_Suitable_for_events
+amen_Private_living_room
+amen_Private_entrance
+amen_Lock_on_bedroom_door
+amen_Fire_extinguisher
+amen_Smoking_allowed
+amen_Safety_card
+amen_Hot_tub
+amen_Buzzer_wireless_intercom
+amen_Wheelchair_accessible
+amen_Air_conditioning
+amen_Doorman
+amen_Self_Check_In
+amen_Smartlock
+amen_Keypad
+amen_Lockbox
+amen_Doorman_Entry
+amen_Pool
+amen_Washer_Dryer
+amen_Free_parking_on_street
+amen_Paid_parking_off_premises
,data=data_amen)
summary(NSV)

NSC<-lm(review_scores_cleanliness~
+amen_Kitchen
+amen_Washer
+amen_Smoke_detector
+amen_Family_kid_friendly
+amen_Essentials
+amen_Carbon_monoxide_detector
+amen_Indoor_fireplace
+amen_Dryer
+amen_First_aid_kit
+amen_24_hour_check_in
+amen_Hair_dryer
+amen_Iron
+amen_Breakfast
+amen_Shampoo
+amen_Pets_allowed
+amen_Gym
+amen_Pets_live_on_this_property
+amen_Suitable_for_events
+amen_Private_living_room
+amen_Private_entrance
+amen_Lock_on_bedroom_door
+amen_Fire_extinguisher
+amen_Smoking_allowed
+amen_Safety_card
+amen_Hot_tub
+amen_Buzzer_wireless_intercom
+amen_Wheelchair_accessible
+amen_Air_conditioning
+amen_Doorman
+amen_Self_Check_In
+amen_Smartlock
+amen_Keypad
+amen_Lockbox
+amen_Doorman_Entry
+amen_Pool
+amen_Washer_Dryer
,data=data_amen)
summary(NSC)


PRICE<-lm(price_pp~amen_Wireless_Internet
+amen_Kitchen
+amen_Washer
+amen_Smoke_detector
+amen_Laptop_friendly_workspace
+amen_TV
+amen_Internet
+amen_Free_parking_on_premises
+amen_Elevator_in_building
+amen_Heating
+amen_Family_kid_friendly
+amen_Essentials
+amen_Carbon_monoxide_detector
+amen_Hangers
+amen_Cable_TV
+amen_Indoor_fireplace
+amen_Dryer
+amen_First_aid_kit
+amen_24_hour_check_in
+amen_Hair_dryer
+amen_Iron
+amen_Breakfast
+amen_Shampoo
+amen_Pets_allowed
+amen_Gym
+amen_Pets_live_on_this_property
+amen_Suitable_for_events
+amen_Private_living_room
+amen_Private_entrance
+amen_Lock_on_bedroom_door
+amen_Fire_extinguisher
+amen_Smoking_allowed
+amen_Safety_card
+amen_Hot_tub
+amen_Buzzer_wireless_intercom
+amen_Wheelchair_accessible
+amen_Air_conditioning
+amen_Doorman
+amen_Self_Check_In
+amen_Smartlock
+amen_Keypad
+amen_Lockbox
+amen_Doorman_Entry
+amen_Pool
+amen_Washer_Dryer
+amen_Free_parking_on_street
+amen_Paid_parking_off_premises
,data=data_amen)
summary(PRICE)

```

```{r}
NOR<-lm(number_of_reviews~
amen_Internet
+amen_Wireless_Internet		
+amen_Heating		
+amen_Kitchen		
+amen_Essentials
+amen_Washer		
+amen_Smoke_detector		
+amen_TV		
+amen_Hangers		
+amen_Iron
,data=data_amen)
summary(NOR)

NSR<-lm(review_scores_rating~
amen_Internet
+amen_Wireless_Internet		
+amen_Heating		
+amen_Kitchen		
+amen_Essentials
+amen_Washer		
+amen_Smoke_detector		
+amen_TV		
+amen_Hangers		
+amen_Iron
,data=data_amen)
summary(NSR)

NSV<-lm(review_scores_value~
amen_Internet
+amen_Wireless_Internet		
+amen_Heating		
+amen_Kitchen		
+amen_Essentials
+amen_Washer		
+amen_Smoke_detector		
+amen_TV		
+amen_Hangers		
+amen_Iron
,data=data_amen)
summary(NSV)

PRICE<-lm(price_pp~
            amen_Internet
+amen_Wireless_Internet		
+amen_Heating		
+amen_Kitchen		
+amen_Essentials
+amen_Washer		
+amen_Smoke_detector		
+amen_TV		
+amen_Hangers		
+amen_Iron
,data=data_amen)
summary(PRICE)
```

```


##Test

This is for test. 

## MY Sandbox

This is where I do analysis
