---
title: "AirBnB in London - Finding the right price"
author: "Nina Hauser, Lingyao Li, Jingyin Qiu, Ching Ci Chen, Petr Perina, Alexander Dziwisch"
date: "13.10.2017"
output:
  html_document:
    number_sections: yes
    css: style.css
    includes:
      before_body: doc_prefix.html
      after_body: doc_end.html
bibliography: bibliography.bib
csl: harvard-imperial-college-london.csl
---

```{r message=FALSE, echo=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(pracma)
library(sp)
library(rgdal)
library(knitr)
library(stringr)
library(formattable)
library(nortest)
library(stargazer)
library(gridExtra)
library(car)
library(plyr)

load("data_short.RData")

lnd <- readOGR(dsn = "map_data", layer = "london_sport", verbose = FALSE)
lnd_f <- broom::tidy(lnd)
```

# Introduction

Moving to a new city on a tight budget is challenging. Especially, a metropolis like London has high rents and a competitive market that makes it difficult to find accommodation that has the right attributes at the right price. Sharing economy services such as AirBnB have faciliated the search for a spare room rented out by a private agent. The available rooms and apartments are available for the user to settle right in. But how do you know if the price you are paying for your flat is actually a fair price?

This paper aims to create a model which will identify how much AirBnB guests value different attributes of London rooms. The guests can also refer to in order to check whether they are paying an appropriate price for their AirBnB.

# Description of the dataset

The dataset of this paper covers all AirBnB offerings in London as per the 4th and 5th of March 2017. It contains 53,904 observations for 95 different variables. Its source is the website "Inside AirBnB - Adding data to the debate" [@Cox_2017]. This is an independent and non-commercial project aiming to examine the effect of AirBnB activities on urban development.

To allow this investigation to be more focused, the dataset was narrowed down. Only private rooms with at least three valid ratings were included. The resulting dataset has 6,495 observations for 78 variables and will be described further in the following section.

## Price

```{r echo = FALSE}
price_desc <- broom::tidy(round(summary(data_short$price)))
colnames(price_desc) <- c("Min", "Q1", "Median", "Mean", "Q3", "Max")

formattable(price_desc, caption = "Table 1: Descriptives of the Price")
```

Since price is the dependent variable of our investigation, it is very important. The summary statistics show that 75% of all AirBnBs are priced at £59 per night or less. However, there are some severe outliers that range up to a maximum of £590.

This raises concerns about the normality of its distribution. In fact, the plot to the left shows the distribution is not normal. The plot to the right hand side shows that if a logarithmic scale is used for the price, it looks almost normally distributed.

```{r, echo=FALSE, fig.width=10, fig.height=3.5, fig.cap="Figure 1: Density of Price and ln(Price)"}
p1 <- data_short %>% ggplot(aes(x = price)) + geom_density(fill = "#00E5FFFF", alpha = .5, color = NA) + labs(x = "PRICE", y = "DENSITY") + 
  theme_minimal() + geom_vline(xintercept = mean(data_short$price), col = "#4C00FFFF")
p2 <- data_short %>% ggplot(aes(x = price_log)) + geom_density(fill = "#00E5FFFF", alpha = .5, color = NA) + labs(x = "LN(PRICE)", y = "DENSITY") + 
  theme_minimal() + geom_vline(xintercept = mean(data_short$price_log), col = "#4C00FFFF")

grid.arrange(p1, p2, ncol = 2, widths = c(1.5, 1))
```

## Rent

With London being one of the most expensive cities to live, rent prices can be considered a major cost of being a host on AirBnB. Therefore, we would like to observe the relationship between rent and the AirBnB price to account for the impact of rent on price. The initial dataset holds no information on the regular rent price at the location of an AirBnB. Fortunately, a website called “Find Properly” [see @Findproperly_2017]  utilizes the data from Zoopla and provides the rent and selling price for each London region, divided per post code. Using the post code, we were able to map the average weekly rent for 1-bed properties to every AirBnB. The matching was done based on the first half of the post code.

Mapping the mean rent and the logarithmically transformed AirBnB price according to their location reveals that those variables are related. Nevertheless, it also becomes clear that there is more to an AirBnB price than just the average rent in the particular neighbourhood.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, fig.cap="Figure 2: Mapping Rent Prices vs. AirBnB Prices"}
map1 <- ggplot() +
  geom_polygon(data = lnd_f, aes(long, lat, group = group), fill = "grey95", color = "grey32") +
  geom_point(data = data_short, aes(east, north, color = mean_rent), alpha = 0.5, size = 1) +
  labs(x = 'Easting', y = 'Northing') +
  coord_equal() + theme_minimal() + scale_colour_gradientn(colours = topo.colors(4)) + theme(legend.position = "bottom")

map2 <- ggplot() +
  geom_polygon(data = lnd_f, aes(long, lat, group = group), fill = "grey95", color = "grey32") +
  geom_point(data = data_short, aes(east, north, color = price_log), alpha = 0.5, size = 1) +
  labs(x = 'Easting', y = 'Northing') +
  coord_equal() + theme_minimal() + scale_colour_gradientn(colours = topo.colors(4))  + theme(legend.position = "bottom")

grid.arrange(map1, map2, ncol = 2)
```

## Location

```{r echo=FALSE}
t1 <- cor.test(data_short$distance, data_short$price_log)
t1_summary <- data.frame(p_value = round(t1$p.value, 2), conf_low = round(t1$conf.int[1], 2), estimate = round(t1$estimate, 2), conf_high = round(t1$conf.int[2],2))

colnames(t1_summary) <- c("P-Value", "Conf-Int. Low", "Estimate", "Conf-Int. High")

formattable(t1_summary, caption = "Table 2: Descriptives of Location")
```

When choosing an AirBnB in London, location is an important factor, since staying close to the city centre is prefered by many. In our model, we use the distance to the touristic city centre - Picadilly Circus - as a simple proxy of the attractiveness of the AirBnB's location. It was calculated by using the Haversine formula [see @Reid_2011] and the geographic coordinates of Picadilly Circus (Longitude: -0.133869, Latitude: 51.510067).

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=3.5, fig.cap="Figure 3: Mapping Rent Prices vs. AirBnB Prices"}
cuts <- data.frame(price_log = data_short$price_log, dist_bin = cut(data_short$distance, 10))

cuts %>% ggplot() + geom_boxplot(aes(x = dist_bin, y = price_log), fill = "#00E5FFFF", alpha = .5, color = "#333333") + theme_minimal() + coord_flip() + scale_x_discrete(limits = rev(levels(cuts$dist_bin))) +
  ylab("LN(PRICE)") + xlab("DISTANCE")
```

From the boxplot and correlation test above, it seems that the distance to the city center and price are significantly negatively correlated. That means that, statistically speaking, the closer the property is to the city center, the higher the price is.

## Reviews

In addition to the written reviews, guests can give their hosts star-ratings on the following parameters [see @Airbnb_2017]: Overall experience, accuracy, cleanliness, communication, check in, location and value. Most of those are self-explanatory; accuracy represents the extent to which the online listing represtents the reality, and value is a subjective measure of whether the room was worth the price paid.

The guest ratings are translated into a score out of 10 for the individual categories, and a score out of 100 for the overall score. The mean value for many categories is 9 or 10. Such high scores are frequently seen when feedback from users is collected. For example, Uber considers removing drivers rated on average less than 4.6 stars out of 5 [@BI_2015].

Since the overall score is submitted independently, rather than calculated from the category scores, it is interesting to see which categories affect the user's overall rating the most. The correlation of the overall score and value, check in and accuracy is very high, suggesting that those categories matter the most for the guest's overall satisfaction. The correlation with price hints that location of the AirBnB is an important determinants of price, as the location rating is highly correlated with the price.

```{r echo=FALSE}
#This code creates a nice looking table! Just change the name and content of the columns!
descriptives_rating <- data.frame(
                 Name=c("Accuracy", "Check In", "Cleanliness", 
                        "Communication", "Location", "Value", "Overall"),
                 
                 Minimum=c(min(data_short$review_scores_accuracy), 
                           min(data_short$review_scores_checkin),
                           min(data_short$review_scores_cleanliness),
                           min(data_short$review_scores_communication),
                           min(data_short$review_scores_location), 
                           min(data_short$review_scores_value), 
                           min(data_short$review_scores_rating)),
                 
                 Maximum=c(max(data_short$review_scores_accuracy), 
                           max(data_short$review_scores_checkin),
                           max(data_short$review_scores_cleanliness), 
                           max(data_short$review_scores_communication), 
                           max(data_short$review_scores_location), 
                           max(data_short$review_scores_value),
                           max(data_short$review_scores_rating)), 
                 
                 Mean=c(round(mean(data_short$review_scores_accuracy)),
                        round(mean(data_short$review_scores_checkin)), 
                        round(mean(data_short$review_scores_cleanliness)),
                        round(mean(data_short$review_scores_communication)), 
                        round(mean(data_short$review_scores_location)), 
                        round(mean(data_short$review_scores_value)),
                        round(mean(data_short$review_scores_rating))),
                 
                 Correlation_Rating=c(round(cor(data_short$review_scores_rating, data_short$review_scores_accuracy, 
                                                use = "complete.obs"),2),
                               round(cor(data_short$review_scores_rating, data_short$review_scores_cleanliness, use = "complete.obs"),2),
                               round(cor(data_short$review_scores_rating, data_short$review_scores_checkin, use = "complete.obs"),2),
                               round(cor(data_short$review_scores_rating, data_short$review_scores_communication, use = "complete.obs"),2),
                               round(cor(data_short$review_scores_rating, data_short$review_scores_location, use = "complete.obs"),2),
                               round(cor(data_short$review_scores_rating, data_short$review_scores_value, use = "complete.obs"),2),
                               1),
                 
                 Correlation_Price=c(round(cor(data_short$price_log, data_short$review_scores_accuracy, use = "complete.obs"),2),
                               round(cor(data_short$price_log, data_short$review_scores_cleanliness, use = "complete.obs"),2),
                               round(cor(data_short$price_log, data_short$review_scores_checkin, use = "complete.obs"),2),
                               round(cor(data_short$price_log, data_short$review_scores_communication, use = "complete.obs"),2),
                               round(cor(data_short$price_log, data_short$review_scores_location, use = "complete.obs"),2),
                               round(cor(data_short$price_log, data_short$review_scores_value, use = "complete.obs"),2),
                               round(cor(data_short$price_log, data_short$review_scores_rating, use = "complete.obs"),2)))

formattable(descriptives_rating, caption = "Table 3: Descriptives of Rating")
```

## Property Characteristics

### Accomodates and Beds

```{r echo=FALSE}
t1 <- cor.test(data_short$price_log, data_short$accommodates)
t2 <- cor.test(data_short$price_log, data_short$beds)

t_summary <- data.frame(names = c("Accomodates", "Beds"), p_value = c(round(t1$p.value,2), round(t2$p.value,2)), conf_low = c(round(t1$conf.int[1], 2), round(t2$conf.int[1], 2)), estimate = c(round(t1$estimate,2), round(t2$estimate,2)), conf_high = c(round(t1$conf.int[2], 2), round(t2$conf.int[2],2)))

colnames(t_summary) <- c("Variable", "P-Value", "Conf-Int. Low", "Estimate", "Conf-Int. High")

formattable(t_summary, caption = "Table 4: Descriptives of Space")
```

The variables accomodates (how many people can stay in the property) and beds (the number of beds in the property) give an indication of the overall capacity of the AirBnB. Although the price mostly includes only one guest, a more spacious flat can be expected to be more expensive. Therefore, one may expect increasing prices for higher values of these variables.

Running a two-sided correlation shows a significant and positive linear effect on the logarithmic price for both variables.

### Amenities

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5.5, fig.cap="Figure 4: Count of Amenities"}
amen <- select(data_short, contains("amen_"))

amen<-rename(amen,c("amen_Internet"="Internet","amen_Wireless_Internet"="Wifi","amen_Heating"="Heating","amen_Kitchen"="Kitchen","amen_Essentials"="Essentials","amen_Washer"="Washer","amen_Smoke_detector"="Smoke_detector","amen_Shampoo"="Shampoo","amen_Hangers"="Hangers","amen_Iron"="Iron","amen_TV"="TV","amen_Hair_dryer"="Hair_dryer","amen_Carbon_monoxide_detector"="Carbon_monoxide_detector","amen_Laptop_friendly_workspace"="Laptop_friendly","amen_Family/kid_friendly"="Family_friendly","amen_Buzzer/wireless_intercom"="Buzzer_wireless","amen_Dryer"="Dryer","amen_First_aid_kit"="First_aid_kit","amen_Elevator_in_building"="Elevator_in_building","amen_Fire_extinguisher"="Fire_extinguisher","amen_24-hour_check-in"="24_hour_check_in","amen_Free_parking_on_premises"="Free_parking","amen_Breakfast"="Breakfast","amen_Cable_TV"="Cable_TV","amen_Lock_on_bedroom_door"="Lock_on_bedroom_door","amen_Safety_card"="Safety_card","amen_Smoking_allowed"="Smoking_allowed","amen_Pets_live_on_this_property"="Pets_live_here","amen_Hot_tub"="Hot_tub","amen_Wheelchair_accessible"="Wheelchair_accessible","amen_Pets_allowed"="Pets_allowed","amen_Indoor_fireplace"="Indoor_fireplace","amen_Doorman"="Doorman","amen_Keypad"="Keypad","amen_Free_parking_on_street"="Free_parking_on_street","amen_Paid_parking_off_premises"="Paid_parking","amen_Smartlock"="Smartlock","amen_Washer_/_Dryer"="Washer_Dryer","amen_Air_conditioning"="Air_con","amen_Self_Check-In"="Self_Check-In","amen_Gym"="Gym","amen_Lockbox"="Lockbox","amen_Suitable_for_events"="Suitable_for_events","amen_Private_entrance"="Private_entrance","amen_Private_living_room"="Private_living_room","amen_Pool"="Pool","amen_Doorman_Entry"="Doorman_Entry"))

amen_name <- colnames(amen)
number <- colMeans(amen[, (1:53)], na.rm=TRUE) * 100
amen_data <- as.data.frame(amen_name)
amen_data$number = number

amen_data <- amen_data[-c(6,17,18,21,36,45,51),]
amen_data <- amen_data %>% filter(number <= 91 & number >= 15)
amen_data <- arrange(amen_data , desc(number))

amen_data %>% ggplot() + geom_bar(aes(x = reorder(amen_name, number), y = number), fill = "#00E5FFFF", alpha = .5, stat = 'identity', width = 1) + coord_flip() + theme_minimal() + ylab("NUMBER") + xlab("AMENITY")
```

AirBnB includes some general information on the property such as the room type, the number of people that can be accommodated or the number of bathrooms. On top of these characteristics, AirBnB contains information on a wide range of amenities for every flat. These range from the availability of Internet and a TV to a personal doorman or a pool. In order to analyse these, we introduced dummy variables for 53 different amenities, with 46 resulting in usable data, as well as a variable counting the total number of amenities.

We found 6 amenities which influence the price, including some home essentials such as a TV, a dryer, and a washer and facilities like an elevator. Also, whether the room has a door lock and whether it is a family- and kid-friendly environment matters. The presence of a TV, an elevator, a dryer or a washer tends to have a positive impact on the flat's price, this is especially true for the TV. Interestingly, it seems that AirBnBs that have a kitchen and a lock on the bedroom door seem to be slightly less valued. Perhaps a lock on the bedroom door is more commonly in place in less safe locations.

```{r echo = FALSE}
t1 <- t.test(data_short[data_short[, "amen_Washer"] == "TRUE", "price_log"], 
       data_short[data_short[, "amen_Washer"]  == "FALSE", "price_log"])
t2 <- t.test(data_short[data_short[, "amen_TV"] == "TRUE", "price_log"], 
       data_short[data_short[, "amen_TV"]  == "FALSE", "price_log"])
t3 <- t.test(data_short[data_short[, "amen_Family/kid_friendly"] == "TRUE", "price_log"], 
       data_short[data_short[, "amen_Family/kid_friendly"]  == "FALSE", "price_log"])
t4 <- t.test(data_short[data_short[, "amen_Dryer"] == "TRUE", "price_log"], 
       data_short[data_short[, "amen_Dryer"]  == "FALSE", "price_log"])
t6 <- t.test(data_short[data_short[, "amen_Elevator_in_building"] == "TRUE", "price_log"], 
       data_short[data_short[, "amen_Elevator_in_building"]  == "FALSE", "price_log"])
t7 <- t.test(data_short[data_short[, "amen_Lock_on_bedroom_door"] == "TRUE", "price_log"], 
       data_short[data_short[, "amen_Lock_on_bedroom_door"]  == "FALSE", "price_log"])

t_data <- data.frame(amenities = c("Washer", "TV", "Familiy / Kid-Friendly", "Dryer", "Elevator in Building", "Lock on Bedroom Door"), P_Value = c(round(t1$p.value, 2), round(t2$p.value,2), round(t3$p.value,2), round(t4$p.value, 2), round(t6$p.value,2), round(t7$p.value,2)), Mean_Without = c(round(t1$estimate[1],2), round(t2$estimate[1],2), round(t3$estimate[1],2), round(t4$estimate[1],2), round(t6$estimate[1],2), round(t7$estimate[1],2)), Mean_With = c(round(t1$estimate[2],2), round(t2$estimate[2],2), round(t3$estimate[2],2), round(t4$estimate[2],2), round(t6$estimate[2],2), round(t7$estimate[2],2)))

t_data <- t_data %>% mutate(Difference = Mean_With - Mean_Without)

formattable(t_data, caption = "Table 5: Descriptives of Selected Amenities")
```


## Attributes of the ad

In this part, we are going to analyse the attributes of the ad. Based on our intuition, we chose 2 variables that may influence the price - whether the AirBnB is instantly bookable and the strictness of its cancellation policy. 

Usually, a guest needs to submit a booking request and he/she gets to stay in the property only if the host approves that request. To attract more customers, some hosts allow instant booking of their properties, which is similar to booking a hotel - the user just books the property straight away. In our dataset, TRUE means guests can book the desired property instantly, while FALSE means they have to get approval from the host first.

In addition to instant book, hosts also have the right to choose their own cancellation policy. Cancellation policy determines whether or not guests can get a refund and how they can be refunded. There are several cancellation policies form which hosts can choose, including flexible, moderate, strict and super strict. If flexible, guests may get a full refund if the reservation is cancelled within a limited period, typically 24 hours prior to the check in. If moderate, fees are fully refundable but only if cancelled a longer time in advance. Under the strict policy, only 50% of fees may be refunded if the booking is cancelled more than 1 week before check in.

```{r echo=FALSE}
t1 <- t.test(data_short[data_short[, "instant_bookable"] == "TRUE", "price_log"], 
       data_short[data_short[, "instant_bookable"]  == "FALSE", "price_log"])

t2 <- cor.test(as.numeric(data_short$cancellation_policy), data_short$price_log)

t_data <- data.frame(attributes = c("Instant Bookable", "Cancellation Policy"), p_vals = c(signif(t1$p.value, 4), signif(t2$p.value, 4)))

formattable(t_data, caption = "Table 6: Descriptives of Ad Properties")
```

To attract more customers, hosts sometimes  allow instant booking of their properties. While TRUE means guests can book the desired property instantly, FALSE means they have to discuss their plans with the host and wait for approval before they can book. 
In addition to instant booking, hosts also have the right to choose their own cancellation policy. The cancellation policy decides whether guests can get a refund and how they can be refunded after they cancel a booking. There are several cancellation policies form which hosts can choose, including flexible, moderate, strict and super strict. If the policy is flexible, guests may get a full refund if the reservation is cancelled within limited period, mostly 24 hours prior to the check-in. If it is moderate, fees are fully refundable if it is cancelled one week before the arrival. Under a strict policy, only 50% of fees may be refunded as long as the cancellation is conducted one week prior to check-in.

# Regression model

```{r echo=FALSE, results='asis'}
m1 <- lm(price_log ~ mean_rent +
                          distance +
                          accommodates + 
                          review_scores_rating +
                          review_scores_cleanliness +
                          review_scores_location +
                          beds +
                          `amen_Family/kid_friendly` +
                          amen_TV +
                          amen_Elevator_in_building +
                          amen_Dryer +
                          amen_Kitchen +
                          amen_Washer +
                          amen_Lock_on_bedroom_door +
                          instant_bookable +
                          cancellation_policy,
         data = data_short)

m2 <- lm(price_log ~ mean_rent +
           distance +
           accommodates + 
           review_scores_rating +
           review_scores_cleanliness +
           review_scores_location +
           amen_TV +
           amen_Elevator_in_building +
           amen_Dryer,
         data = data_short)

stargazer(list(m1,m2), type = "html", single.row = TRUE,  title="Table 7: Regression Results",  dep.var.labels=c("Ln Price"), covariate.labels=c("Mean Rent", "Distance", "Accomodates","Review Score - Rating", "Review Score - Cleanliness", "Review Score - Location", "Number of Beds", "Amenity - Family friendly", "Amenity - TV", "Amenity - Elevator", "Amenity - Dryer", "Amenity - Kitchen", "Amenity - Washer", "Amenity - Lock on Bedroom Door", "Instant bookable - FALSE", "Cancellation Policy - Moderate", "Cancellation Policy - Strict"))
```

## Interpretation

As our dependent variable was transformed to its logarithmic version, a log-linear regression model is used to explain the effect of the independent variables on the dependent variable. Some of the amenities had a negative impact on the price, which is conterintuitive. As the effects are small and likely to be caused by random noise, such variables are excluded. Additionally, only variables that are significant for the regression are kept in the model:

$$\begin{gather*} ln(price) =  \beta_0 + \beta_1(mean\_rent) + \beta_2(distance) + \beta_3(accomodates) + \\ \beta_4(review\_scores\_rating) + \beta_5(review\_scores\_cleanliness) + \beta_6(review\_scores\_location) + \\ \beta_7(TV) + \beta_8(elevator) + \beta_9(dryer) + u \end{gather*}$$

41.8 percent of the variation of the observations can be explained with the presented regression model. The standard error of the model in absolute currency is approximately 1.36 GBP off from the real value and the F-statistic is highly significant. Thus, the model provides a far better explanation than just the fit intercept model.The y-intercept is located at 6.88 GBP. However, there will not be an apartment that does have a rent of zero or can accomodate no one. Therefore, the intercept has to used rather carefully. The other coefficients are explaining by how many percentage points the price changes if the explanatory variable changes by one unit holding all other independent variables constant. For example, for every additional person a room can accomodate, the price rises by 6.8 percent. The former, the review scores for location as an indicator for attractiveness of the neighbourhood and amenities like the existence of a TV, elevator and dryer have the largest postive effects on the price of a room. The review scores of value had to be taken out of the regression because the inherint endogenity problem: Price is a large factor in determining the review of a guest regarding the price for value. The effect of distance is surprisingly small. This impies that distance to city center is not the best measure to account for geographic differences. 

## Fitting the model

```{r echo=FALSE}
data_model <- data.frame(price = data_short$price, price_log = data_short$price_log, residuals = m2$residuals)


high_residuals <- data_model %>%
  select(price, price_log, residuals) %>%
  filter(residuals > 0.3)

low_residuals <- data_model %>%
  select(price, price_log, residuals) %>%
  filter(residuals <= 0.3)

descriptives_residuals <- data.frame(
                 Name=c("Data with high residuals", "Data with low residuals"),
                 
                 LN_Mean_Rent=c(round(mean(high_residuals$price_log), 2), round(mean(low_residuals$price_log),2)),
                 
                 Mean_Rent=c(round(mean(high_residuals$price), 2), round(mean(low_residuals$price),2)))

colnames(descriptives_residuals) = c("Name", "Ln Mean Rent", "Mean Rent")

formattable(descriptives_residuals, caption = "Table 8: Residuals")
```

A short exploration of the residuals shows that with rising prices, the residuals increase. This implies that our model is worse in predicting the more expensive rooms as the factors chosen do not fully explain the difference in price. The relation between residuals and prices may be explained by a factor the model could not quantify: the attractiveness of the room and the house it is in. As this attractiveness differs across buildings and sometimes even within a building, it is impossible to predict the price of an apartment that exceeds expectations set by the base explanatory variables used in the regression.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, fig.cap="Figure 5: Residuals and Prediction"}

data_model <- data.frame(price = data_short$price, price_log = data_short$price_log, predicted = m2$fitted.values, residuals = m2$residuals)

p1 <- ggplot(data = data_model, aes(x = predicted, y= residuals)) +
  geom_point(col = "#00E5FFFF", alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, col ="#4C00FFFF") +
  theme_minimal() + xlab("PREDICTED") + ylab("RESIDUALS")

p2 <- ggplot(data = data_model, aes(x = predicted, y = price_log)) +
  geom_point(col = "#00E5FFFF", alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, col ="#4C00FFFF") +
  theme_minimal() + xlab("PREDICTED") + ylab("LN(PRICE)")

grid.arrange(p1, p2, ncol = 2)
```

## Limitations of our model

Due to the scope of this assignment we were not able to address every issue with our data. Several issues and will be discussed here.

### Omitted variable bias

The price of an AirBnB is affected by a large number of factors. We built a model that includes some of them, but it was not feasible to include data concerning every single possible determinant. As a result, our model likely suffers from omitted variable bias. It under- or overestimates the effect of some of the existing factors to compensate for the missing information, making our model less reliable. Our dataset doesn't contain several important variables, such as the size of the room, the proximity of the flat to a tube station, the age of the flat,the quality of the equipment and furniture in the flat or the attractiveness of the apartment and the building.

### Multicollinearity

Upon testing for multicollinearity, correlations between the explanatory variables become clear. Those relations might increase the error terms of the model. A VIF of four implies that the variance of the estimators in the model are four times higher than if the independent variables were uncorrelated. Usually, a VIF greater than 5 is considered critical to the model results. None of the used variables reaches that border value. The Durbin-Watson test shows that the error values are uncorrelated, as visible in the plot of residuals against predicted values.

```{r echo=FALSE}
t1 <- vif(m2)
t1_data = data.frame(VIF = round(t1, 2))
rownames(t1_data) = c("Mean Rent", "Distance", "Accomodates", "Review Score - Rating", "Review Score - Cleanliness", "Review Score - Location", "Amenity - TV", "Amenity - Elevator", "Amenity - Dryer")
formattable(t1_data, caption = "Table 9: Results Multicollinearity Test")

```
```{r echo=FALSE}
t2 <- durbinWatsonTest(m2)
t2_data <- data.frame(round(t2$r, 2), round(t2$dw, 2), round(t2$p, 2))
colnames(t2_data) <- c("Autocorrelation", "D-W Statistic", "p-value")
formattable(t2_data, caption = "Table 10: Results Durbin Watson Test")
```


### Sensitivity to outliers

As in any regression model based on ordinary least squares, the coefficients in our model are affected by outliers. Some of the properties in our data set cost more than \$400 per night, while most of them cost below \$100. The outliers may have disproportionately affect our coefficients, making them less accurate for the remaining variables.

### Non-linear relationships

Some of our explanatory variables (for example the distance from the city center) are not linearly related with the price of the property. There is a significant difference between the average price of a room located right in the city center and 5km away, while the difference for rooms located 25km away and 30km away is not very large. This suggests that we could model the relationship more accurately if we used non-linear regression.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data = data_short, aes(x = distance, y = price_log)) + geom_smooth(se = FALSE) + theme_classic() + xlab("DISTANCE") + ylab("LN(PRICE)")
```

### Lack of clustering

By putting all properties into one model, we ignore the fact that there might be different profiles of properties and for each profile, different characteristics might be relatively more important. Perhaps there is a set of properties that are popular with students coming to London for graduate job interviews, who would see location close to the financial centers and low price as important factors. And, perhaps, different types of properties are popular with middle-aged tourists - then the proximity to the popular sights and the level of comfort provided might matter more. If we divided our properties into clusters which share similar characteristics, and then ran a regression analysis for each cluster, we might get a more accurate model for each cluster.

# Conclusion

Despite the fact that the presented model has obvious limitations regarding factors that could not be quantified, it has direct implications for finding a reasonably prices apartment. Many attributes important for someone searching for a room, like WiFi and the existence of a proper equipped kitchen, have small effects on the room price, as they are present in most London apartments. A traveller can therefore expect to have those properties present. Luxury amenities like the presence of an elevator, a TV and a dryer create costs. Depending on the standards of the guest, these can be added if the budget is extended. It is also good advice to check apartments in less attractive neighbourhoods to save money. Regarding cleanliness, a well maintained room will cost more. Looking at these different attributes of an AirBnB ad, the user is able to determine whether the price of the apartment is actually fair, which was the aim of this report. As especially high prices could not be explained in the model, a prediction is likely to return a base price rather than a highly attractive room in a good apartment in a nice building.

# Bibliography