---
title: "Airbnb in London - Finding the right price"
author: "Nina Hauser, Lingyao Li, Jingyin Qiu, Ching Ci Chen, Petr Perina, Alexander Dziwisch"
date: "13.10.2017"
output:
  html_document:
    number_sections: yes
    css: style.css
    includes:
      before_body: doc_prefix.html
      after_body: doc_end.html
bibliography: bibliography.bib
csl: harvard-imperial-college-london.csl
---

```{r message=FALSE, echo=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(pracma)
library(sp)
library(rgdal)
library(knitr)
library(stringr)
library(formattable)
library(nortest)
library(stargazer)
library(gridExtra)

load("data_short.RData")

lnd <- readOGR(dsn = "map_data", layer = "london_sport", verbose = FALSE)
lnd_f <- broom::tidy(lnd)
```

# Introduction

Moving to a new city on a tight budget is challenging. Especially, a metropolis like London has high rents and a competitive market that makes it difficult to find accommodation that has the right attributes at the right price. Sharing economy services like Airbnb have faciliated the search for a spare room rented out by private agent. The available rooms and apartments are furnished for the user to settle right in. But how do you know if the price you are paying for your flat is actually a fair price?

Profits of both hosts and the platform itself have skyrocketed in the past years. A typical UK host earns around £3,000 a year [@Indi_2017]. It is certain that profit comes from the user that is paying both the fee of the platform and the profit margin of the host out of his own pocket. If you are on a tight budget yourself you want to pick a price that is market average with the attributes important to you. This paper aims at creating a model to forecast the price a user pay will pay per night for an Airbnb matching his requirements to faciliate the check whether the price of the apartment is indeed the fair price. 

# Description of the dataset

The dataset for this investigation covers all Airbnb offerings in London as per the 4th and 5th of March 2017. It contains 53,904 observations for 95 different variables. Its source is the website "Inside Airbnb - Adding data to the debate" [@Cox_2017]. This is an independent and non-commercial project aiming to examine the effect of Airbnb activities on urban development.

To allow this investigation to be more focused, the dataset was narrowed down. For example, only private rooms with at least three valid ratings were included. The resulting dataset has 6,495 observations for 78 variables and will be described in the following section.

## Price

```{r echo = FALSE}
price_desc <- broom::tidy(summary(data_short$price))
colnames(price_desc) <- c("Min", "Q1", "Median", "Mean", "Q3", "Max")

formattable(price_desc, caption = "Table 1: Summary of Price Variable")
```

Since price is the dependent variable of our investigation, it is very important. The summary statistics show that 75% of all Airbnbs are priced at £59 per night or less. However, there are some severe outliers that range up to a maximum of £590.

This raises concerns about the normality of its distribution. In fact, the plot to the left shows the distribution is not normal. The plot to the right hand side shows that if a logarithmic scale is used for the price, it looks almost normally distributed.

```{r, echo=FALSE, fig.width=10, fig.height=3.5, fig.cap="Figure 1: Density of Price and Log10 of Price"}
p1 <- data_short %>% ggplot(aes(x = price)) + geom_density(fill = "#00E5FFFF", alpha = .5, color = NA) + labs(x = "PRICE", y = "DENSITY") + 
  theme_minimal() + geom_vline(xintercept = mean(data_short$price), col = "#4C00FFFF")
p2 <- data_short %>% ggplot(aes(x = price_log)) + geom_density(fill = "#00E5FFFF", alpha = .5, color = NA) + labs(x = "PRICE - Log10", y = "DENSITY") + 
  theme_minimal() + geom_vline(xintercept = mean(data_short$price_log), col = "#4C00FFFF")

grid.arrange(p1, p2, ncol = 2, widths = c(1.5, 1))
```

## Rent

With London being one of the most expensive cities to live, rent prices can be considered a major cost of being a host on AirBnB. Therefore, we would like to observe the relationship between rent and the AirBnB price. However, the initial dataset holds no information on the regular rent price at the location of an Airbnb. Fortunately, a website called “Find Properly” [see @Findproperly_2017]  utilizes the data from Zoopla and provides the rent and selling price for each London region, divided per post code. Using the post code, we were able to map the average weekly rent for 1-bed properties to every AirBnB. The matching was done based on the first half of the post code.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, fig.cap="Figure 2: Mapping Rent Prices vs. Airbnb Prices"}
map1 <- ggplot() +
  geom_polygon(data = lnd_f, aes(long, lat, group = group), fill = "grey95", color = "grey32") +
  geom_point(data = data_short, aes(east, north, color = mean_rent), alpha = 0.5, size = 1) +
  labs(x = 'Easting', y = 'Northing') +
  coord_equal() + theme_minimal() + scale_colour_gradientn(colours = topo.colors(4)) + theme(legend.position = "bottom")

map2 <- ggplot() +
  geom_polygon(data = lnd_f, aes(long, lat, group = group), fill = "grey95", color = "grey32") +
  geom_point(data = data_short, aes(east, north, color = price_log), alpha = 0.5, size = 1) +
  labs(x = 'Easting', y = 'Northing') +
  coord_equal() + theme_minimal() + scale_colour_gradientn(colours = topo.colors(4))  + theme(legend.position = "bottom")

grid.arrange(map1, map2, ncol = 2)
```

Mapping the mean rent and the logarithmically transformed AirBnB price according to their location reveals that those variables are related. Nevertheless, it also becomes clear that there is more to an AirBnB price than just the average rent in the particular neighbourhood.

## Location

```{r echo=FALSE}
t1 <- cor.test(data_short$distance, data_short$price_log)
t1_summary <- data.frame(p_value = t1$p.value, conf_low = t1$conf.int[1], estimate = t1$estimate, conf_high = t1$conf.int[2])

colnames(t1_summary) <- c("P-Value", "Conf Low", "Estimate", "Conf High")

formattable(t1_summary, caption = "Table 1: Summary of Price Variable")
```

When choosing an AirBnB in London, location might be an important factor as for many users living close to the city centre is preferable. In our model, we use the distance to the touristic city centre - Picadilly Circus - as a measurement of the attractiveness of the AirBnB's location. It was calculated by using the Haversine formula [see @Reid_2011] and the geographic coordinates of Picadilly Circus (Longitude: -0.133869, Latitude: 51.510067).

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=3.5, fig.cap="Figure 3: Mapping Rent Prices vs. Airbnb Prices"}
cuts <- data.frame(price_log = data_short$price_log, dist_bin = cut(data_short$distance, 10))

cuts %>% ggplot() + geom_boxplot(aes(x = dist_bin, y = price_log), fill = "#00E5FFFF", alpha = .5, color = "#333333") + theme_minimal() + coord_flip() + scale_x_discrete(limits = rev(levels(cuts$dist_bin)))
```

From the boxplot and correlation test above, it seems that distance to the city center and price are significantly negatively correlated. That means that, statistically speaking, the closer the property is to the city center, the higher the price is.

## Reviews

Additionally to the written reviews, guests can give their hosts star-ratings on the following parameters [see @Airbnb_2017]: Overall experience, accuracy, cleanliness, communication, check in, location and value. Overall experience relates to the general impression of the guest and is only calculated for ads with at least three reviews. Accuracy asks how well the ad represented the real properties of the apartment. Cleanliness accounts for tidiness of the flat. Check in and communication are both service-based: Was communication with the host before and during the stay sufficient and was the check in process smooth or difficult? The location is evaluated based on security, comfort and attractiveness of the neighbourhood. Finally, value is a subjective measure to define whether the guests believe that the apartment is worth the price paid - an interesting measure for our analysis.

While the guest gives his or her ratings on a one-to-five-star scale, the data set transforms this data to a rating from 1 to 10, for the overall rating from 0 to 100. In the table below, the average of reviews is very high: At either 9 or 10 for the subrating scores and at 92 for the overall score. Reviews start at values 2 or 4 for the subcategories and 20 for the overall rating. This means, that ads with good ratings are overrepresented suggesting ads with bad reviews will be unlikely to be booked and, therefore, removed from the website. {search for academic paper to prove statement!} As the overall score is individually picked, different subcategories have different effects on the overall rating. Overall score is only moderately correlated to location, communication and cleanliness. Accuracy, check in and value are strongly correlated to the points received in overall rating. Transferring these findings to the analysis implies a higher impact of those  variables on the model and shows the necessity to analyse both subcategories and overall rating score as they are given independently. The relation between the different rating scores and price is relatively weak. For none of the categories there is even a weak correlation to price. 

```{r echo=FALSE}
#This code creates a nice looking table! Just change the name and content of the columns!
descriptives_rating <- data.frame(
                 Name=c("Accuracy", "Check In", "Cleanliness", 
                        "Communication", "Location", "Value", "Overall"),
                 
                 Minimum=c(min(data_short$review_scores_accuracy), 
                           min(data_short$review_scores_checkin),
                           min(data_short$review_scores_cleanliness),
                           min(data_short$review_scores_communication),
                           min(data_short$review_scores_location), 
                           min(data_short$review_scores_value), 
                           min(data_short$review_scores_rating)),
                 
                 Maximum=c(max(data_short$review_scores_accuracy), 
                           max(data_short$review_scores_checkin),
                           max(data_short$review_scores_cleanliness), 
                           max(data_short$review_scores_communication), 
                           max(data_short$review_scores_location), 
                           max(data_short$review_scores_value),
                           max(data_short$review_scores_rating)), 
                 
                 Mean=c(round(mean(data_short$review_scores_accuracy)),
                        round(mean(data_short$review_scores_checkin)), 
                        round(mean(data_short$review_scores_cleanliness)),
                        round(mean(data_short$review_scores_communication)), 
                        round(mean(data_short$review_scores_location)), 
                        round(mean(data_short$review_scores_value)),
                        round(mean(data_short$review_scores_rating))),
                 
                 Correlation_Rating=c(round(cor(data_short$review_scores_rating, data_short$review_scores_accuracy, 
                                                use = "complete.obs"),2),
                               round(cor(data_short$review_scores_rating, data_short$review_scores_cleanliness, use = "complete.obs"),2),
                               round(cor(data_short$review_scores_rating, data_short$review_scores_checkin, use = "complete.obs"),2),
                               round(cor(data_short$review_scores_rating, data_short$review_scores_communication, use = "complete.obs"),2),
                               round(cor(data_short$review_scores_rating, data_short$review_scores_location, use = "complete.obs"),2),
                               round(cor(data_short$review_scores_rating, data_short$review_scores_value, use = "complete.obs"),2),
                               1),
                 
                 Correlation_Price=c(round(cor(data_short$price_log, data_short$review_scores_accuracy, use = "complete.obs"),2),
                               round(cor(data_short$price_log, data_short$review_scores_cleanliness, use = "complete.obs"),2),
                               round(cor(data_short$price_log, data_short$review_scores_checkin, use = "complete.obs"),2),
                               round(cor(data_short$price_log, data_short$review_scores_communication, use = "complete.obs"),2),
                               round(cor(data_short$price_log, data_short$review_scores_location, use = "complete.obs"),2),
                               round(cor(data_short$price_log, data_short$review_scores_value, use = "complete.obs"),2),
                               round(cor(data_short$price_log, data_short$review_scores_rating, use = "complete.obs"),2)))

formattable(descriptives_rating, caption = "Table 1: Summary of Price Variable")
```

## Property Characteristics and Amenities

```{r eval=FALSE}
amen <- select(data_short, contains("amen_"))
amen_name <- colnames(amen)
number <- colMeans(amen[, (1:53)], na.rm=TRUE) * 100
amen_data <- as.data.frame(amen_name)
amen_data$number = number
amen_data <- amen_data[-c(6,17,18,21,36,45,51),]
amen_data <- arrange(amen_data , desc(number))

amen_data %>% ggplot() + geom_bar(aes(x = reorder(amen_name, number), y = number), stat = 'identity') + coord_flip()
```

Airbnb includes some general information on the property such as the room type, the number of people that can be accommodated or the number of bathrooms. On top of these characteristics, Airbnb contains information on a wide range of amenities for every flat. These range from the availability of Internet and a TV up to a personal doorman or a pool. In order to analyse these, we introduced dummy variables for 52 different amenities as well as a variable counting the total number of amenities.

There are 97% of the rooms offering Wifi and internet connection. Besides, some general amenities for houses such as heating facilities (96%), kitchens (91%), essentials (85%), washers (81%), shampoo(62%), hangers (61%), and Iron (56%), will often be provided in houses/rooms. However, in London, most of the offerings don’t allow their customers to smoke and to bring their pets with them. 77% of rooms are with smoke detectors, and only 10% of rooms are smoking allowed and pets allowed. Due to the weather in London, air-con facility seems not important, but this will be a must in most of the Asian countries. 



```{r eval=FALSE}
library(plyr)
rating<-list("number_of_reviews","review_scores_rating","review_scores_value")
rating1<-unlist(rating)
amen_list<-list(amen_name)
amen_list1<-unlist(amen_list)
data.cor<-select(data_short,contains("amen_"),price,number_of_reviews,review_scores_rating,review_scores_value,review_scores_cleanliness)%>%filter(!is.na(number_of_reviews),!is.na(review_scores_rating),!is.na(review_scores_value),!is.na(review_scores_cleanliness))
data_amen1<-rename(data.cor,c("amen_24-hour_check-in"="amen_24_hour_check_in","amen_Washer_/_Dryer"="amen_Washer_Dryer","amen_Family/kid_friendly"="amen_Family_kid_friendly","amen_Buzzer/wireless_intercom"="amen_Buzzer_wireless_intercom","amen_Cat(s)"="amen_Cat","amen_Dog(s)"="amen_Dog","amen_Other_pet(s)"="amen_Other_pet","amen_Self_Check-In"="amen_Self_Check_In"))
data_amen<-filter(data_amen1,price<100)
data_amen2<-filter(data_amen1,review_scores_rating>=80)
data_amen3<-filter(data_amen1,review_scores_value>=8)
data_amen4<-filter(data_amen1,review_scores_cleanliness>=8)
data_amen5<-filter(data_amen1,number_of_reviews<=50)

```

### Key ameniteis to influence the price

There are around 49 offers of amenities in the AirBnB in London. Out of 49 amenities offerings, we found 7 amenities may influence the price, including some home essentials such as kitchens, TVs, dryers, and washers, facilities like elevators or whether it’s a family-kid friendly environment as well as whether it provides lock on the bedroom door. The price of the accommodation with TVs, elevators, dryers and washers is higher than those don’t, especially for TV, which may lead to higher overall rating and perceived value from customers (Please refer to the plot between the amenity and rating below. Since most of the ratings are above 80 or 8, we do filter the rooms with rating more than 80 or 8 to see the difference. People tend to rate the room among higher range, mostly above 90 or 9. Therefore, some drop from 10 to 9 should already be significant.)  However, it seems the market doesn’t value those accommodations with family-kid friendly environment and kitchen. Their prices are slightly lower than those without those amenities. Probably, those amenities linked to more work and noisy. Another interesting finding is the room without the lock can may have higher price than others, which may be reasoned that the room with lock may mainly in more unsafe regions.


```{r eval=FALSE}
ggplot(data_amen,aes(x=amen_Family_kid_friendly,y=price))+geom_boxplot()
ggplot(data_amen,aes(x=amen_TV,y=price))+geom_boxplot()
ggplot(data_amen,aes(x=amen_Elevator_in_building,y=price))+geom_boxplot()
ggplot(data_amen,aes(x=amen_Dryer,y=price))+geom_boxplot()
ggplot(data_amen,aes(x=amen_Kitchen,y=price))+geom_boxplot()
ggplot(data_amen,aes(x=amen_Washer,y=price))+geom_boxplot()
ggplot(data_amen,aes(x=amen_Lock_on_bedroom_door,y=price))+geom_boxplot()
```

```{r eval=FALSE}

ggplot(data_amen2,aes(x=amen_TV,y=review_scores_rating))+geom_boxplot()
ggplot(data_amen2,aes(x=amen_Elevator_in_building,y=review_scores_rating))+geom_boxplot()
ggplot(data_amen2,aes(x=amen_Family_kid_friendly,y=review_scores_rating))+geom_boxplot()
ggplot(data_amen2,aes(x=amen_Dryer,y=review_scores_rating))+geom_boxplot()
ggplot(data_amen2,aes(x=amen_Kitchen,y=review_scores_rating))+geom_boxplot()
ggplot(data_amen2,aes(x=amen_Washer,y=review_scores_rating))+geom_boxplot()
ggplot(data_amen2,aes(x=amen_Lock_on_bedroom_door,y=review_scores_rating))+geom_boxplot()


```

```{r eval=FALSE}
ggplot(data_amen3,aes(x=amen_TV,y=review_scores_value))+geom_boxplot()

```

+ <strong>Property Characteristics:</strong> Some general information on the property such as the room type, the number of people that can be accommodated or the number of bathrooms.
+ <strong>Amenities:</strong> On top of the characteristics, Airbnb contains information on a wide range of amenities for every flat. These range from the availability of Internet and a TV up to a personal doorman or a pool. We introduced dummy variables for 52 different amenities as well as a variable counting the total number of amenities.
+ <strong>Offering Characteristics:</strong> Lastly some information on the Cancellation Policy or whether the Airbnb is instantly bookable was included.


Furthermore, the Cartesian coordinates were calculated, using the instructions of @Irawan_2014, to plot the data on maps provided by @lovelace2014introduction.


# Bibliography