---
title: "jingyin_test"
author: "Jingyin"
date: "September 27, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This is where I will do my analysis and I will put the interesting stuff in Final_report.Rmd
hahhahah  hope it work

```{r}
library(ggplot2)
library(stargazer)
```


###Descriptive Statistics ###

#3. Location#
When choosing an Airbnb in London, people may consider its location since location decides the convenience to travel around or live in London. In our model, we use the distance to city center, Westminster, as a measurement of the Airbnb location. People normally expected that the closer to the city center, the higher the Airbnb rent.

```{r}
ggplot(data_short, aes(distance)) + 
  geom_density() +
  theme_minimal() +
  geom_vline(xintercept = mean(data_short$distance), col = "red") 
summary(data_short$distance)
#quantile(data_short$distance, c(.95))

```

#correlation between location and price

```{r}
data_short$distance_cut<- cut(data_short$distance, seq(0, 30, 1), labels = c("0-1", "1-2", "2-3", "3-4","4-5","5-6","6-7","7-8","8-9","9-10","10-11","11-12","12-13","13-14","14-15","15-16","16-17","17-18","18-19","19-20","20-21","21-22","22-23","23-24","24-25","25-26","26-27","27-28","28-29","above 29-30"))
data_short$distance_cut[is.na(data_short$distance_cut)] <- "above 29-30"

ggplot(data_short, aes(x = distance_cut, y = price)) + 
  geom_boxplot() +
  theme(axis.text = element_text(angle = 90, hjust =1)) + ylim(0,200)

ggplot(data_short, aes(x = distance_cut, y = price_pp)) + 
  geom_boxplot() +
  theme(axis.text = element_text(angle = 90, hjust =1)) + ylim(0,100)

cor.test(data_short$distance, data_short$price)
```
From the boxplot and correlation test above, the relationship between distance to the city center and price is significantly negatively correlated. Statistically speaking, the closer to the city center, the higher the price.



###The regression model###
#Description - show the linear one and then the log one and discuss#


```{r}
#copy from "regression_model.R"
rent_data <- read.csv("Price_rent_0927.csv")
rent_data <- rent_data %>% group_by(zip_first = toupper(zipcode)) %>% summarise(n = n(), mean_rent = mean(rent))
data_short <- merge(data_short, rent_data, by="zip_first")
```

```{r}
m0 <- lm(price ~ mean_rent +
           distance +
           accommodates + 
           review_scores_rating +
           review_scores_cleanliness +
           review_scores_location +
           review_scores_value +
           beds +
           `amen_Family/kid_friendly` +
           amen_TV +
           amen_Elevator_in_building +
           amen_Dryer +
           amen_Kitchen +
           amen_Washer +
           amen_Lock_on_bedroom_door +
           instant_bookable +
           cancellation_policy,
         data = data_short)

m1 <- lm(log10(price) ~ mean_rent +
                          distance +
                          accommodates + 
                          review_scores_rating +
                          review_scores_cleanliness +
                          review_scores_location +
                          beds +
                          `amen_Family/kid_friendly` +
                          amen_TV +
                          amen_Elevator_in_building +
                          amen_Dryer +
                          amen_Kitchen +
                          amen_Washer +
                          amen_Lock_on_bedroom_door +
                          instant_bookable +
                          cancellation_policy,
         data = data_short)

m2 <- lm(log10(price) ~ mean_rent +
           distance +
           accommodates + 
           review_scores_cleanliness +
           review_scores_location +
           amen_TV +
           amen_Elevator_in_building +
           amen_Dryer,
         data = data_short)

stargazer(list(m1,m2), type = "text")
```

#Interpretation
As our dependent variable had to be transformed to it's logarithmic version, a log-linear regression model is used to explain the effect of the independent variables on the dependent variable. Some of the amendities had a negative impact on the price, which is conterintuitive. As the effects are small and likely to be caused by random noise, such variables are excluded. Additionally, only variables that are significant for the regression are kept in the model:

$$ y =  \beta_0 + \beta_1(mean\_rent) + \beta_2(distance) + \beta_3(accomodates) + \beta_4(review\_scores\_rating) + \beta_5(review\_scores\_cleanliness) + \beta_6(review\_scores\_location) + \beta_7(TV) + \beta_8(elevator) + \beta_9(dryer) + u$$
41.8 percent of the variation of the observations can be explained with the presented regression model. Even though residuals are high, the F-statistic is highly significant and the model provides a far better explanation than just the coefficient value.The y-intercept is located at 9.1411 GBP. However, there will not be an apartment that does have a rent of zero or can accomodate no one. Therefore, the intercept has to used rather carefully. The other coefficients are explaining by how many percentage points y changes if $$x_i$$ changes by one unit. For example, for every additional person a room can accomodate, y rises by 6.7 percent. The former, the review scores for location as an indicator for attractiveness of the neighbourhood and amenities like the existence of a TV, elevator and dryer have the largest postive effects on the price of a room. The review scores of value had to be taken out of the regression because the inherint endogenity problem: Price is a large factor in determining the review of a guest regarding the price for value. Interestingly, the effect of distance is small and negative. Firstly, this impies that distance to city center is not the best measure to account for geographic differences. Secondly, concurrence in the city center could be responsible for the negativity: With a rising amount of rooms available, prices are under pressure. 

---------------------------------Above----------------------------------------------



```{r}
#price_filt <- data_short %>% filter(price_pp <100 )
data_short$price_cut <- cut(data_short$price_pp, seq(0, 150, 10), labels = c("0-10", "11-20", "21-30", "31-40", "41-50", "51-60", "61-70", "71-80", "81-90", "91-100", "101-110", "111-120", "121-130", "131-140", "141-150"))

#filter the distance < 18.08827, (95%) and price_pp <150
data_short %>% filter(distance < 18, price_pp<150) %>%
  ggplot(aes(distance)) + geom_density()

data_short$distance_cut<- cut(data_short$distance, seq(0, 18, 1), labels = c("0-1", "1-2", "2-3", "3-4","4-5","5-6","6-7","7-8","8-9","9-10","10-11","11-12","12-13","13-14","14-15","15-16","16-17","17-18"))
data_short %>% filter(distance < 18, price_pp<150) %>%
  ggplot(aes(x = distance_cut, y = price_pp)) + 
  geom_boxplot() 

#labels = c("0-1", "1-2", "2-3", "3-4","4-5","5-6","6-7","7-8","8-9","9-10","10-11","11-12","12-13","13-14","14-15","15-16","16-17","17-18","18-19","19-20","20-21","21-22","22-23","23-24","24-25","25-26","26-27","27-28","28-29","29-30", "30-31","31-32","32-33","33-34","34-35","35-36","36-37","37-38","38-39","39-40"))

```
#cut left -half
#cut into"center","middle" "outter"
#inter-column
# most expensive neighbourhood in london, compare with the rest
```{r}
toupper(Price_rent_0927$zipcode)
```

Catogarize each erea according to the average rent in different zipcode.

```{r}
Price_rent_cat <-
  Price_rent_0927 %>% 
  group_by(zipcode) %>% 
  summarise(avg_rent = mean(rent)) %>%
  mutate(rank_rent = rank(desc(avg_rent))) %>%
  arrange(rank_rent)


a <- nrow(Price_rent_cat) * 1/4
b <- nrow(Price_rent_cat) * 2/4
c <- nrow(Price_rent_cat) * 3/4
d <- nrow(Price_rent_cat)


Price_rent_cat <- Price_rent_cat %>% mutate( tier = ifelse(rank_rent %in% floor(c(1:a)), "tier1", ifelse(rank_rent %in% floor(c(a:b)), "tier2", ifelse(rank_rent %in% floor(c(b:c)), "tier3", ifelse(rank_rent %in% floor(c(c:d+1)), "tier4","" )))))

```