---
title: "For_now"
author: "Lingyao"
date: "2017/9/27"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
library(ggplot2)
library(dplyr)
load("data_short.RData")
```

In this part, we are going to analyse attributes of the ad. We choose 2 variables that we think may influence price_pp intuitively, which includes whether it is instant bookable and cancellation policy. 

# instant_bookable
To attract more customers, sometimes hosts allow instant book of their properties. In terms of instant book, there are 2 kinds of accommodation. In our dataset, TRUE means guests can book the desired property instantly, while FALSE means they have to discuss their plans with the host and wait for approval before they can book. 

```{r}
summary(data_short$instant_bookable)
cor.test(as.numeric(data_short$instant_bookable), 
         data_short$price_pp)
ggplot(data = data_short, aes(x = instant_bookable, y = price_pp)) + geom_boxplot() + labs(x = "Instant Bookable", y = "Price Per Person") 
t.test(data_short[data_short[, "instant_bookable"] == "TRUE", "price_pp"], 
       data_short[data_short[, "instant_bookable"]  == "FALSE", "price_pp"])
```
Despite the fact that instant book will make the booking process more convient for both hosts and guests, there are only about 26.5% of hosts adopt it.  
From the Pearson's product-moment correlation test, its relatively low correlation shows there is not very linear relation between instant bookability and price pp, while the t-test for means suggests otherwise. If we look at the boxplot, we can see that in general price_pp is higher if the accommodation cannot be booked instantly. The resut does make sense in practice. Under the circumstances where the rent is relatively high, hosts are more likely not to implement instant-book policy in order to protect their property.

# cancellation_policy

In addition to instant book, hosts also have the right to choose their own cancellation policy. Cancellation policy decides whether or not guests can get refund and how they can be refunded. There are several cancellation policies form which hosts can choose, including flexible, moderate, strict and super strict. If flexible, guests may get full refund if the reservation is cancelled within limited period, mostly 24 hours prior to the check in. If moderate, fees are fully refundable but within a longer time period. Under the circumstances of strict policy, only 50% of fees may be refunded until 1 week prior to check in. 
(reference and citation may be needed here, url: https://www.airbnb.co.uk/home/cancellation_policies#strict)

```{r}
summary(data_short$cancellation_policy)
cor.test(as.numeric(data_short$cancellation_policy),
         data_short$price_pp)
ggplot(data_short, aes(x = cancellation_policy, y=price_pp)) + geom_boxplot() + labs(x = "Cancellation Policy", y = "Price Per Person") 
```

Surprisingly, accommondations with strict cancellation policy in general have lower price than others. One possible reason might be that with strict policy, hosts' profits are more secure so that they 

Now we want to analyse if there is any correlation between these 2 variables.

```{r}
cor.test(as.numeric(data_short$instant_bookable), as.numeric(data_short$cancellation_policy))
ggplot(data = data_short, aes(x = cancellation_policy, fill = instant_bookable)) + geom_bar(position = "dodge") + labs(x = "Cancellation Policy", y = "Count") 
```
As we can see, a larger propotion of apartments with srict cancellation policy are instant bookable, compared with those with other cancellation policies. 


# beds
The variable beds describes how many deds are available for guests. With more beds available, the price of an accommodation should be higher when setting other parameters equal, if we think about it intuitively. But how exactly does the number of beds influence the price?

```{r}
summary(data_short$beds)
cor.test(data_short$beds, data_short$price)
ggplot(data_short, aes(x = beds)) + geom_bar() + labs(x = "The Number of Beds", y = "Count") 
ggplot(data_short, aes(x = as.factor(beds), y = price)) + geom_boxplot() + labs(x = "The Number of Beds", y = "Price") 
```
With most of the accommondations having less than three beds, we can still observe a clear positive relation between the number of beds and price, which matches our expectation. In general, the more beds there are, the higher the price is. Since there are not much data for those with more than three beds, we cannot predict the price of them prcisely.