---
title: "Petr's sandbox"
author: "Petr Perina"
date: "September 27, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
load('./data_short.RData')
```
## Limitations of our model

Due to the scope of this assignment we were not able to address every issue with our data. Several issues and will be discussed here.

### Omitted variable bias
The price of an AirBnB is affected by a large number of factors. We built a model that includes some of them, but it was not feasible to include data concerning every single possible determinant. As a result, our model likely suffers from omitted variable bias. It under- or overestimates the effect of some of the existing factors to compensate for the missing information, making our model less reliable. Our dataset doesn't contain several important variables, such as the size of the room, the proximity of the flat to a tube station, the age of the flat or the quality of the equipment and furniture in the flat.

### Multicollinearity
Some of the independent variables in our model are also correlated. For example, consider the correlation of the review score for location and the distance from the city center.

### Sensitivity to outliers

As in any regression model based on ordinary least squares, the coefficients in our model are affected by outliers. Some of the properties in our data set cost more than \$400 per night, while most of them cost below \$100. The outliers may have disproportionately affect our coefficients, making them less accurate for the remaining variables.

### Non-linear relationships

Some of our explanatory variables (for example the distance from the city center) are not linearly related with the price of the property. There is a significant difference between the average price of a room located right in the city center and 5km away, while the difference for rooms located 25km away and 30km away is not very large. This suggests that we could model the relationship more accurately if we used non-linear regression.

```{r}
ggplot(data = data_short, aes(x = distance, y = price)) + geom_smooth()
```

### Lack of clustering

By putting all properties into one model, we ignore the fact that there might be different profiles of properties and for each profile, different characteristics might be relatively more important. Perhaps there is a set of properties that are popular with students coming to London for graduate job interviews, who would see location close to the financial centers and low price as important factors. And, perhaps, different types of properties are popular with middle-aged tourists - then the proximity to the popular sights and the level of comfort provided might matter more. If we divided our properties into clusters which share similar characteristics, and then ran a regression analysis for each cluster, we might get a more accurate model for each cluster.

### Multicollinearity

Some of the independent variables in our model are also correlated. For example, consider the correlation of the review score for location and the distance from the city center.

```{r}
cor(data_short$amen_Washer, data_short$amen_Dryer)
```

Those variables provide similar information to the model and as a result, the standard error of our coefficients is inflated. This also intuitively makes sense as many washers can be used for drying.


