---
title: "Petr's sandbox"
author: "Petr Perina"
date: "September 27, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Limitations of our model

Due to the scope of this assignment we were not able to address every issue with our data. Several issues and will be discussed here.

### Sensitivity to outliers

As in any regression model based on ordinary least squares, the coefficients in our model are affected by outliers. Some of the properties in our data set cost more than \$400 per night, while most of them cost below \$100. The outliers may have disproportionately affect our coefficients, making them less accurate for the remaining variables.

### Non-linear relationships

Some of our explanatory variables (for example the distance from the city center) are not linearly related with the price of the property. There is a significant difference between the average price of a room located right in the city center and 5km away, while the difference for rooms located 25km away and 30km away is not very large. This suggests that we could model the relationship more accurately if we did not use linear regression.

```{r}
ggplot(data = data_short, aes(x = distance, y = price)) + geom_smooth()
```

### Lack of clustering

By putting all properties into one model, we ignore the fact that there might be different profiles of properties and for each profile, different characteristics might be relatively more important. Perhaps there is a set of properties that are popular with students coming to London for graduate job interviews, who would see location close to the financial centers and low price as important factors. And, perhaps, different types of properties are popular with middle-aged tourists - then the proximity to the popular sights and the level of comfort provided might matter more. If we divided our properties into clusters which share similar characteristics, and then ran a regression analysis for each cluster, we might get a more accurate model for each cluster.

### Omitted variable bias
The price of an AirBnB is affected by a large number of factors. We built a model that includes some of them, but it was not feasible to include data concerning every single possible determinant. As a result, our model likely suffers from omitted variable bias. It under- or overestimates the effect of some of the existing factors to compensate for the missing information, making our model less reliable. Our dataset doesn't contain several important variables, such as the size of the room, the proximity of the flat to a tube station, the age of the flat or the quality of the equipment and furniture in the flat.

### Multicollinearity
Some of the independent variables in our model are also correlated. For example, consider the correlation of the review score for location and the distance from the city center. 
```{r}
cor(data_short$amen_Washer, data_short$amen_Dryer)
```

Those variables provide similar information to the model and as a result, the standard error of our coefficients is inflated. This also intuitively makes sense as many washers can be used for drying.

### Heteroscedasticity
I guess leave for Nina to test?


Multicollinearity -> higher error terms
Omitted variable bias (provide examples)
Is our data homoskedastic? Check that the variance of prices is the same across different levels of independent variables








# Old stuff

library("dplyr")
library("ggplot2")
load("data.Rdata")

# select relevant variables
attributes_data <- select(data, property_type, beds, bed_type, bathrooms, bedrooms, room_type, amenities, square_feet, accommodates, price)

glimpse(attributes_data)
str(attributes_data)

# check for missing values
summary(data)
# property_type - 6 factor values, 267 have a value "Other"
# beds have 173 NAs
# bed_type - 5 factor values, no "other"
# bathrooms - 260 NAs
# bedrooms - 93 NAs
# room_type - 3 factor values, no NAs
# amenities - list of amenities, some have translation missing, 685 have an empty list, 
# square_feet - only 582 out of 53904 observations include square_feet info
# accommodates - 1 to 16, no NAs

# check how they correlate with price, especially room type (flat/room), accommodates
# limit only to apartments in property_type?

# turn prices into integers first
data$price <- as.numeric(sub('\\$','',as.character(data$price)))
attributes_data$price <- as.numeric(sub('\\$','',as.character(attributes_data$price)))

# now explore scatter/boxplots
ggplot(data = data) + geom_boxplot(aes(x = room_type, y = price))

# cut accommodate into intervals for plotting
data$acc_cut <- cut(data$accommodates, c(0,1,2,3,4,6,8,10,16))
ggplot(data = data) + geom_boxplot(aes(x = acc_cut, y = price))
# as expected price goes up with more people accommodated

# now let's look at price per person
data$price_pp <- data$price / data$guests_included

ggplot(data = data) + geom_boxplot(aes(x = acc_cut, y = price_pp))
# this is interesting - price per person increases up until 8 guests staying

# obviously accommodates and guests_included are different, compare the above with this
# accommodates seems to be higher - is it max capacity and guests is the actual number of guests?
data$price_pp <- data$price / data$accommodates

ggplot(data = data) + geom_boxplot(aes(x = acc_cut, y = price_pp)) + ylim(0, 200)

# explore property_type
unique(data$property_type)
summary(data$property_type)
# 27 factor values, includes Igloo & Cave :) 267 are "Other"

# explore amenities in more detail
summary(data$amenities)
# each row has a list of amenities, not sure how to simply work with that
# I'm guessing we can check if amenity is in the list and that should work
# we could also "unroll" them into additional rows but that's not practical
# https://stackoverflow.com/questions/19693328/r-how-to-expand-a-row-containing-a-list-to-several-rows-one-for-each-list-m
# dataset would have ~5-10 times more rows

head(data$amenities)
"Cable TV" %in% data$amenities[0]
"Kitchen" %in% data$amenities[0]
data$amenities[0]
# using %in% doesn't work properly - doesn't search through the list

# Visualization
library(ggplot2)

# Look at top property types
property_type_viz <- group_by(attributes_data, property_type) 
property_type_viz %>% summarise(freq = n()) %>% mutate(rank = rank(freq)) %>% 
  filter(rank > 20) %>% arrange(-rank) -> b

ggplot(b, aes(x = property_type, y = freq)) + geom_bar(stat = "identity")

reorder(b$property_type, b$property_type, length)

ggplot(attributes_data, aes(x = attributes_data$property_type)) + geom_bar()
unique(attributes_data$property_type)

# run a regression with our variables, note R^2, see which ones matter, make plots
data$property_type <- factor(data$property_type)
data$bed_type <- factor(data$bed_type)

data$amenities_n <- NA

data$amenities[5]
a <- as.character(data$amenities[5])
find("Kitchen", a)

# for (i in 1:data$amenities){
#   data$amenities_n[i] <- sapply(gregexpr(",", data$amenities[i]), length) + 1
# }
# leave amenities out 

# regression with 0.52 adjusted R^2
fit1 <- lm(data$price ~ data$property_type + data$beds + data$bathrooms + data$bedrooms + data$room_type + data$accommodates)
summary(fit1)
# interestingly bed_type doesn't seem to matter, most property types don't matter either -> limit to those that do

# look at data only for apartments as those are the most frequent property_type
apt_data <- filter(attributes_data, property_type == "Apartment")
str(apt_data)
# re-run the regression, adj R^2 = 0.47, beds are not significant
fit2 <- lm(apt_data$price ~ apt_data$bathrooms + apt_data$beds + apt_data$bedrooms + apt_data$room_type + apt_data$accommodates)
summary(fit2)

# remove beds, adj R^2 = 0.47 and all variables are significant
fit3 <- lm(apt_data$price ~ apt_data$bathrooms + apt_data$bedrooms + apt_data$room_type + apt_data$accommodates)
summary(fit3)

library(usdm)
corr_df <- data.frame(apt_data$bathrooms, apt_data$bedrooms, apt_data$accommodates)
vif(corr_df)
# VIF values are 1.37, 2.27, 2.06 so moderately correlated

# why both private and shared room have a negative impact on price?
# perhaps indicating it is just a room and not an apartment? YES
summary(apt_data$room_type)

# perhaps we should focus on private rooms (n = 15.4k) or entire home/apt (n=22.5k)
# data is a bit confusing - in property_type apartment includes rooms, and in room_type it can be entire home/apt
ggplot(data = apt_data) + geom_boxplot(aes(x = room_type, y = price))

# private room data
pvt_r_data <- filter(apt_data, room_type == "Private room")
pvt_r_data$beds <- cut(pvt_r_data$beds, c(1,2,3,5,7,9,12))
ggplot(data = pvt_r_data) + geom_boxplot(aes(x = bed_type, y = price))

home_data <- filter(apt_data, room_type == "Entire home/apt")
home_data$beds <- cut(home_data$beds, c(1,2,3,5,7,9,12))
ggplot(data = home_data) + geom_boxplot(aes(x = beds, y = price))

# the main variables we'd like to use seem to be bathrooms, bedrooms, private room, shared room, accommodates
# let's see their correlation matrix, remove room type because it's non-numeric
corr_mat_data <- data.frame(apt_data$price, apt_data$bathrooms, apt_data$bedrooms, apt_data$accommodates)
corr_mat <- corr_mat_data[, 2:length(corr_mat_data)]
round(cor(corr_mat_data, use = "pairwise.complete.obs"), 2)
# corr of accommodates and bedrooms 0.69, price and bedrooms 0.51, price & accommodates 0.59

# Checking correlations here
apt_data$bedrooms_cut <- cut(apt_data$bedrooms, c(1,2,3,4,5,6))
ggplot(data = apt_data) + geom_boxplot(aes(x = apt_data$bedrooms_cut, y = apt_data$accommodates))

ggplot(data = apt_data) + geom_boxplot(aes(x = apt_data$bedrooms_cut, y = apt_data$price))

apt_data$accommodates_cut <- cut(apt_data$accommodates, c(1,2,3,4,6,8,10,12,16))
ggplot(data = apt_data) + geom_boxplot(aes(x = apt_data$accommodates_cut, y = apt_data$price))

# Stargazer is a great package for well formatted regression and summary statistics tables



